Missing The Point:

### 2020-07-16 ICML/MissingThePoint.Rmd
Updated presentation with double legend removed

```{css echo=FALSE}
.right-column{
  padding-top: 0;
}
```

@@

```{r echo=FALSE, fig.width=10, fig.height = 5.2, message=FALSE, warning=FALSE}
ggplotly(p_up)
```
]

@@

.pull-right[
<img src="https://raw.githubusercontent.com/gerkovink/shinyMice/edits/shinymicehex.png" width="255">
]
]
<!-- .footnote[Slides created via the R package [**xaringan**](https://github.com/yihui/xaringan).] -->

>>>>

```{css echo=FALSE}
.right-column{
  padding-top: 0;
}
.remark-slide-number {
  font-size: 10pt;
  margin-bottom: -11.6px;
  margin-right: 10px;
  color: #FFFFFF; /* white */
  opacity: 1; /* default: 0.5 */
}
```

@@

```{r echo=FALSE, fig.width=10, fig.height = 5.2, message=FALSE, warning=FALSE}
ggplotly(p_up)
```
]
---
---
.left-column[ 
```{r echo=TRUE, eval=FALSE}

@@

.pull-right[
<img src="https://raw.githubusercontent.com/gerkovink/shinyMice/edits/shinymicehex.png" width="255">
]
]
